---
title: "Debugging Quone-generated R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Debugging Quone-generated R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Compiler diagnostics

```{r}
library(quone)
diags <- quone::diagnostics("src/Stats/Summary.Q")
quone::show_diagnostics(diags)
```

`show_diagnostics()` routes to RStudio's Problems pane (or the
Positron equivalent) when available, and falls back to a
`cli`-styled block in the terminal otherwise. Each row's `category`
column is a factor over the closed set in LANGUAGE.md section 12.1.

## Source maps and traceback rewriting

When you compile with `sourcemap = TRUE` (the default), the
compiler also emits a `.R.map` sidecar mapping generated R lines to
the originating `.Q` position. `with_sourcemap()` installs a
calling handler so any error captured during `expr` rewrites its
traceback frames back to `.Q` source.

```{r}
quone::build("scores.Q", sourcemap = TRUE)
quone::with_sourcemap(source("scores.R"))
```

`dev_session()` enables `with_sourcemap()` automatically.

## Catching specific categories

```{r}
tryCatch(
  quone::check("bad.Q"),
  quone_type_mismatch = function(cnd) message("type error: ", conditionMessage(cnd))
)
```

## LSP

For real-time diagnostics, hover, completion, and go-to-definition
from any LSP-aware editor, install the LSP and let your editor's
extension drive `quonec lsp`:

```{r}
quone::install_lsp()  # auto-detects vscode, positron, neovim, helix, zed
quone::lsp_status()
```
