---
title: "Packages and roxygen2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Packages and roxygen2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This vignette walks through publishing a Quone project as an R
package whose documentation comes from `#'` doc blocks on the Quone
source.

## A small project

```{r}
library(quone)
quone::create_project("scores")
setwd("scores")

quone::create_module("Stats.Summary", stub_name = "mean_score")
```

Edit `src/Stats/Summary.Q`:

```quone
module Stats.Summary exporting (mean_score)


#' Mean score for a vector.
#' @export
mean_score : Vector Double -> Double
mean_score scores <- mean scores
```

## Document and install

```{r}
quone::document()
quone::install()
```

`document()` builds the project, then runs `roxygen2::roxygenise()`
over the build directory so `NAMESPACE` and `man/*.Rd` are derived
from the Quone-side `#' @export` tags.

## Audit dependencies

```{r}
quone::deps()
quone::licenses()
```

## Publish a `pkgdown` site

```{r}
quone::pkgdown_site()
```
